The human in the loop: volunteer computing as a socio-technical system

### 2016-02-28 Alife16/paper.tex
Rewritten abstract and title
Please @mariosky @unintendedbear @fergunet have a good look.
Refs #99 #100

\title{ Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources 
for Low Cost Distributed Evolutionary Computation}
\author{Juan-J.~Merelo*$^1$, Paloma de las Cuevas $^1$, Pablo
  García-Sánchez $^1$, Mario Garc\'ia-Valdez$^2$\\
\mbox{}\\
$^1$Dept. of Computer Architecture and Technology and CITIC University of Granada \\
$^2$Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana \\
{\tt jmerelo@ugr.es}, {\tt mario@tectijuana.edu.mx}}

@@

\begin{abstract}
Volunteer computing is extensively used 
in science and industry, but it
still has a long way to go in order to become
 a mainstream
technology in the same way the cloud technologies in general have. The
lack of 
general purpose and open source tools with built-in analytics 
could be one of the reasons of why this is so, as well as the lack of
proofs of concept. That is why in this paper we present {\sf NodIO}, a
framework used to create client-server architectures for distributed
evolutionary algorithms, entirely written  
in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser, as well as any other client consuming its REST application
programming interface. The architecture, along with some initial
results on the expected performance and scaling behavior when the
number of users is increased is presented. We also use
the algorithm data to find out what kind of patterns the user behavior
follows by examining the resources they devote to our experiment, and
try to fit them to some statistical distribution to create the bases
of a model of user behavior in volunteer computing experiments of this
kind that can be used by researchers to predict its performance. 
In general, our experiments prove, first, that {\sf NodIO} is a flexible and
low-overhead platform to perform distributed computation experiments
that include volunteers, and then that user behavior follows some patterns,
and, thus, are amenable to a model.
\end{abstract}

@@

>>>>

\title{The human in the loop: volunteer computing as a socio-technical
system}
\author{Juan-J.~Merelo*$^1$, Paloma de las Cuevas $^1$, Pablo
  García-Sánchez $^1$, Mario Garc\'ia-Valdez$^2$\\
\mbox{}\\
$^1$Dept. of Computer Architecture and Technology and CITIC University of Granada \\
$^2$Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana \\
{\tt jmerelo@ugr.es}, {\tt mario@tectijuana.edu.mx}}

@@

\begin{abstract}
Volunteer computing is a form of distributed computing where users
decide on their participation and the amount of time they will
``lend''. This makes them an essential part of the algorithm and of
the performance of the whole system. As a sociotechnical system, this
participation follows some patterns and in this paper we examine the
result of several volunteer distributed evolutionary computation
experiments and try to find out which are those patterns and what
makes an experiment successful or not, including the feedback loop
that is created between the users and the algorithm itself.
\end{abstract}

@@

%%% Local Variables:
%%% ispell-local-dictionary: "english"
%%% End:
